Multi sky-view\\ 3D aerosol distribution recovery

### 2013-08-04 article.tex
Final version

In remote sensing~\cite{Pust2011, Mishchenko2007}, imaging through air
is associated with {\em atmospheric correction}, based on {\em aerosol
  retrieval}. In this discipline, the atmosphere is often assumed to
be plane-parallel, using one-dimensional vertical RT. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Namer2009}. In this paper, however, the medium itself,
at all relevant altitudes is the object of interest.

@@

To deploy such a system on a very large scale will require a long-term
engineering effort. Camera specifications should be set to optimally
recover a wide range of aerosol distributions. This requires a major
theoretic and numerical research.

>>>>

In remote sensing~\cite{Mishchenko2007}, imaging through air
is associated with {\em atmospheric correction}, based on {\em aerosol
  retrieval}. In this discipline, the atmosphere is often assumed to
be plane-parallel, using one-dimensional vertical RT. Consequently
state-of-the-art aerosol retrieval is done in distinct large lateral
blocks~\cite{Martonchikc} with limited height
resolution~\cite{kalashnikova}. We, however, seek 3D
recovery. Atmospheric correction is related to
dehazing~\cite{Namer2009}. In this paper, however, the medium itself,
at all relevant altitudes is the object of interest.

@@

To deploy such a system on a very large scale will require a long-term
engineering effort. Camera specifications~\cite{Pust2011} should be
set to optimally recover a wide range of aerosol distributions. This
requires a major theoretic and numerical research.
